D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-01 ootavacuous.tex
Definition sdep: s/fundamantal/fundamental/
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Section~\ref{sec:For Compilers Using Single-Thread Analysis}
focuses on compilers that restrict their analysis to a single
thread,
Section~\ref{sec:For Compilers Using Global Analysis}
slightly relaxes this single-thread restriction,
Section~\ref{sec:Verifying the Fundamental Property}
verifies the fundamantal property of semantic dependencies,
and
Section~\ref{sec:Outstanding Issues}
discusses a general questions regarding our definitions.

>>>>

Section~\ref{sec:For Compilers Using Single-Thread Analysis}
focuses on compilers that restrict their analysis to a single
thread,
Section~\ref{sec:For Compilers Using Global Analysis}
slightly relaxes this single-thread restriction,
Section~\ref{sec:Verifying the Fundamental Property}
verifies the fundamental property of semantic dependencies,
and
Section~\ref{sec:Outstanding Issues}
discusses a general questions regarding our definitions.
